\chapter{Introduction}

\section{Purpose}
The purpose of this document serves to provide and in-depth analysis into the user characteristics, requirements and use cases for and autonomous drone. 
It will utilize the latest technologies in the industry to detect objects and navigate itself based on the detections. 
The document includes detailed information regarding the requirements of the project.
Furthermore it explains how requirements are to be met.

% This document provides an in depth overview of our plans to implement object recognition, 
% tracking and 2D mapping as part of the FMDS (Follow Me Drones System). 
% The system will be used to aid rangers in the field while scouting areas of suspected poaching/intrusion. 
% A drone employing our software will patrol with the ranger at a safe height while surveying the area 
% for objects which might be of interest to the ranger, thus increasing their efficiency.   

\section{Project Scope}
% $<$Provide a short description of the software being specified and its purpose,
%including relevant benefits, objectives, and goals. Relate the software to
% corporate goals or business strategies. If a separate vision and scope document
%is available, refer to it rather than duplicating its contents here.$>$

The primary aim of the FMDS is to provide support to a ranger in the field by having the drone surveying the surrounding area for objects and sending notifications to the ranger upon identification. This will increase 
the rangers efficiency by providing an aerial overview of the surroundings and identifying objects that the 
ranger could potentially miss.
\newline
\newline
While the drone is surveying, it will periodically take a snapshot of the area for later use in creating a 2D map. 
Any objects (Be it animals, humans or something a human would be carrying on them) that are detected by our object detection
software will have their location recorded and a pin will be dropped on the 2D map. This can be used to detect hotspots for
animals or even poachers.

\section{Definitions, Acronyms and Abbreviations}

FMDS - Follow Me Drones System

%\section{References}


